\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\usepackage{tcolorbox}
\tcbuselibrary{theorems}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
 \usepackage{graphicx}
 \usepackage{titling}

\title{Pezzotto TV Case}
\author{Accusation Legal Team}
\date{}
 
 \usepackage{fancyhdr}
\fancypagestyle{plain}{%  the preset of fancyhdr 
    \fancyhf{} % clear all header and footer fields
    \fancyfoot[L]{\thedate}
    \fancyhead[L]{Law and Computer Science}
    \fancyhead[R]{\theauthor}
}
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  \vskip 1em%
  \begin{center}%
  \let \footnote \thanks
    {\LARGE \@title \par}%
    \vskip 1em%
    %{\large \@date}%
  \end{center}%
  \par
  \vskip 1em}
\makeatother

\begin{document}

\newtcbtheorem[]{mytheo}{dasds}%
{colback=black!5,colframe=black!55!black!80,fonttitle=\bfseries}{th}

\newtcbtheorem[]{class}{Example}%
{colback=purple!5,colframe=purple!55!black!80,fonttitle=\bfseries}{th}

\newtcolorbox{my theorem}[1]{
colback=black!5,colframe=black!55!black!80,fonttitle=\bfseries, title={#1}}

\maketitle

Mr. John Doe is accused of the crime of infringement of copyright having distributed and sold 
devices or elements of special decoding which allows access to an encrypted service without 
paying the fee to the corresponding companies but by acquiring the payment itself.
More precisely, we are referring to Pezzotto TV, with which is pointed to an illegal 
decoder which has the function of downloading and receiving private IPTV at the cost of 
a few euros per month. On the basis of all of this we find Mr. John Doe, who obtains the  
transmision signal from an original subscription for each platform and which, 
after extrapolating it, transmits it illegally to his subscribers. 

\hfill \break
The use of a modified decoder for carrying out this operation makes the accused Mr. John Doe 
punishable under the law of computer fraud, article 640-ter:
\begin{my theorem}{Art. 640 - ter}
  Any alteration of an electronic, 
  computer or telematic device by intervening in any way on data, information or programs 
  contained therein, without the right to do so, procuring for oneself or others an unjust 
  profit with damage to others.
\end{my theorem}

with an aggravating circumstance determined for profit, article 61 - paragraph 7: 

\begin{my theorem}{Art. 61 - paragraph 7}
  Having caused the victim of the crime a serious patrimonial 
  damage in crimes against property, or that in any case offend the property, or in crimes 
  motivated by profit.
\end{my theorem}

and for the crime of unauthorized access to a computer system, article 615 - ter: 

\begin{my theorem}{Art. 615-ter}
  Unauthorized introduction to a computer or telematic system protected
  by security measures, against the expressed or tacit will of those who have the right 
  to exclude it.
\end{my theorem}

\hfill \break
Watching films, sporting events or TV series illegally necessarily implies a violation of 
copyright, for example the law that aims to protect those who create a work, and in particular 
article 171 ter lett. f: 
\begin{my theorem}{Art. 171 ter lett. f}
  Punishes anyone who manufactures, imports, distributes, sells, rents, 
  gives for any reason, advertises for sale or rental, or holds for commercial purposes, equipment, 
  products or components or provides services that have the prevailing purpose or commercial use to 
  avoid effective technological measures pursuant to art. 102 quater, or which are primarily designed,
  manufactured, adapted or performed for the purpose of enabling or facilitating the circumvention 
  of said measures. These technological measures shall comprise the measures that are applied or 
  that remain after certain measures are removed by rightholders voluntarily or by virtue of 
  agreements with the beneficiaries of exceptions, or in compliance with an injunction by 
  an administrative or judicial authority.
\end{my theorem}

and at the same time the article 171 - octies:
\begin{my theorem}{Art. 171 - octies}
  Whoever produces, sales, imports, promotes, installs, modifies, or uses, either 
  for personal or public use, with fraudulent purposes, devices or parts of devices 
  meant to decode conditional-access audiovisual transmissions which have been broadcast 
  by air, satellite or cable, whether in analogue or digital form, shall be punished.
\end{my theorem}

\hfill \break
Thanks to the help of the police, who collected evidence through IP tracing, requesting data 
from local and national Internet Service Providers and reviewing some suspicious electronic 
payments to Pezzotto TV made by unknown users, it was possible to bring the accusation. 
Furthermore, the investigations were also useful for bringing light into the operating 
methods of the criminal association, described as a pyramid-shaped structure, at the 
top of which are subjects who, although not knowing each other directly, establish mutual 
ties to achieve the criminal purpose. According to the reconstruction of the investigators, 
the main phases of the criminal scheme include:
\begin{enumerate}
  \item Legitimate purchase of copyrighted content in the form of digital signals by the top of the
        pyramid (they are referred to as Sources).
  \item Transformation of the contents thus acquired into IT data, through a complex technical 
        and organizational infrastructure.
  \item Broadcast of computer data in the form of audio/video streams through an articulated 
        network of resellers and end users equipped with an internet connection and special 
        equipment - commonly known as \textit{Pezzotto}. To sell subscriptions, the criminal 
        network made use of bots, channels, groups, forums and blogs that
        advertised the offer on the Net; messages were also conveyed via Telegram and social networks.
\end{enumerate}

\hfill \break
Mr. John Doe is required to be present in date 03/05/2023 in the courtroom 02 of Università degli Studi di Roma La Sapienza, Castro Laurenziano street, 7.

\section*{Credits}
  The accusation legal team is composed by:
  \begin{itemize}
    \item Lorenzo Scalera - 1912241
    \item Lucian Dorin Crainic - 1938430 
    \item Miriam Alessandra Muraru - 1935720
    \item Davide Loriga - 1964829
    \item Alessandro Pandolfi - 1887464
    \item Alessandro Candelori - 1943275
    \item Lorenzo Clementi - 1972314
    \item Alejandro Lougedo Patricio - 2055285
    \item Melissa Rueca - 1886929
  \end{itemize}
\end{document}

